% Created 2018-05-29 Tue 12:06
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage[margin=1.0in]{geometry}
\setlength\parindent{0pt}

\author{Richard Cuminale}
\date{Spring 2018}
\title{English 3 Final Exam}
\hypersetup{
 pdfauthor={Richard Cuminale},
 pdftitle={English 3 Final Exam},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.1 (Org mode 9.1.9)}, 
 pdflang={English}}
\begin{document}

\maketitle

Name: \rule{6.0cm}{0.4pt}

\vspace{0.5cm}
Period: \rule{3.0cm}{0.4pt}

\vspace{0.5cm}
\textbf{Parts 1 - 4 are closed notes. Turn in this work before
  beginning the essay portion of the final.} 

\section{Sentence Expansion}
\label{sec:orga557197}
8 points; 2 points each
\vspace{1em}

Define the function of each of the following words, then use each word
in a compound sentence. Sentences must be complete, grammatically
correct, and use proper punctuation and capitalization to earn full
credit. 
\vspace{1em}

\begin{tabular}{lll}
Word & Function & Example\\
\hline
So \vspace{2.0cm} & \hspace{6.0cm}  & \hspace{6.0cm} \\
Because \vspace{2.0cm}&  & \\
Therefore \vspace{2.0cm} &  & \\
However \vspace{2.0cm} &  & \\
\end{tabular}

\newpage
\section{Appositives}
\label{sec:orgfea975e}
6 points; 2 points each
\vspace{1em}

Write three sentences that use appositives correctly.
In each sentence, circle the appositive and underline the noun or
noun phrase it modifies.
Sentences must be complete, grammatically correct, and use proper
punctuation and capitalization to earn full credit.

\vspace{0.5cm}


1.
\vspace{1.5cm}

2.
\vspace{1.5cm}

3.
\vspace{1.5cm}


\section{Narrative Analysis}
\label{sec:org74bc1ce}
25 points; 5 points each
\vspace{1em}

List and define the five narrative elements. 

\vspace{1em}

1.
\vspace{1.0cm}

2.
\vspace{1.0cm}

3.
\vspace{1.0cm}

4.
\vspace{1.0cm}

5.
\vspace{1.0cm}

Describe how to discover the conflict in a narrative:
\vspace{2.5cm}

\newpage
\section{Writing Process}
\label{sec:orga226362}
30 points; 15 points each
\vspace{1em}

Answer the following questions in complete sentences.
\begin{itemize}
\item How does the writing process work recursively, as you write? (If you
draw the diagram, be sure to explain it!) \vspace{6cm}
\item Writing changes from exploratory to clarifying as it moves from
beginning to end.
\begin{itemize}
\item Describe the relationship between exporatory and clarifying
  writing, then draw a chart that illustrates this.
\item In that chart list at least three kind of exploratory writing
and two kinds of clarifying writing.
\end{itemize}\vspace{8cm}
\end{itemize}

\vfill

\begin{center}
\textbf{Turn in your work and then you may take out your notes and
  begin the essay.}
\end{center}

\newpage
\section{Literary Analysis Essay}
\label{sec:orgf9f34cb}
\textbf{``By Any Other Name'' by Santha Rama Rau}
\vspace{1em}

50 points
\vspace{1em}

Read the personal narrative, ``By Any Other Name,'' by Santha Rama
Rau. Using the prompt below, respond in a focused, well organized
essay that has an introduction, conclusion, body paragraphs, and text
evidence.

\vspace{1em}
Essay Prompt: \emph{Analyze the relationship between the two students,
  Santha and Premila, and the British culture they participate
  in. What is this narrative suggesting about British rule of India in
  the early 20th century?}
\vspace{1em}

Note:
\begin{itemize}
\item A focus on characterization and setting will yield the most
  material for your essay.
\item You may want to consider literary elements such as imagery,
  characterization, selection of detail, and structure in your
  response.
\item You may use your annotated story and any other notes or
  organizers prepared prior to the final exam.
\item Include an introduction that gives the context of the essay and
  makes a clear thesis statement. Include the title and author.
\item Be sure to make clear, consistent references to the story in your analysis.
\end{itemize}

\emph{Your essay must be written on the paper provided.}

\vfill

\textbf{Total Score}\hline

\newpage

1\hline
\vfill

2\hline
\vfill

3\hline
\vfill

4\hline
\vfill

5\hline
\vfill

6\hline
\vfill

7\hline
\vfill

8\hline
\vfill

9\hline
\vfill

10\hline
\vfill

11\hline
\vfill

12\hline
\vfill

13\hline
\vfill

14\hline
\vfill

15\hline
\vfill

16\hline
\vfill

17\hline
\vfill

18\hline
\vfill

19\hline
\vfill

20\hline
\vfill

21\hline
\vfill

22\hline
\vfill

23\hline
\vfill

24\hline
\vfill

25\hline
\vfill

\end{document}
